A mechanical Model of Rod-Shaped Bacteria

### 2025-06-19 paper/main.tex
move references to this directory
change path; use local

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{../docs/source/_static/mechanics.png}
    \caption{
        Example of an elonged bacterial rod represented by a collection of vertices which are
        connected by springs.
        The angles $\alpha_i$ have been exaggerated such that they can be identified more easily.
        A bacterial agent which is not interacting with any external objects will tend to the
        equilibrium state of a straight rod with $0$ curvature.
    }
    \label{fig:mechanics-bacterium}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/raw_pv/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/images/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/masks/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \caption{
        (A) shows the raw result from combining sphere and cylinder meshes to obtain the shape of a
        bacterial rod.
        This render contains lighting coming from 2 light sources which thus produces a small glow
        on the upper part of the meshes.
        Subfigure (B) takes this image and applies noise to it in order to make it look more
        like an actual microscopic image.
        (C) The render is projected along the z-axis and flat numerical values are assigned to the
        bacteria.
        The resuling render can have overlaps in which case the color of the rod is displayed that
        is higher along the z-direction.
    }
    \label{fig:progression-image-generation}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/algorithm/image001042.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/algorithm/mask-zoom.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/algorithm/mask-zoom.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \caption{
        TODO change 2nd image!\\
        (A) An example of a microscopic image.
        (B) The associated mask which assigns individual color values to each bacterium.
        (C) The result of the  skeletonization algorithm when applying it to a single cell.
    }
    \label{fig:position-extraction-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-004000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-006000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-008000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.5\textwidth]
        {../docs/source/_static/fitting-methods/displacement-calculations.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {../docs/source/_static/fitting-methods/displacement-distribution.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}
    \caption{
        Progression of generated masks with estimated and exact positions.
        Comparison of masks across generations. Compare estimated with exact rod lengths.
    }
    \label{fig:benchmarking-extraction-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-1.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-2.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \linebreak
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-3.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-4.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}
    \caption{
        The figure shows two masks (A,B) which will be compared against each other.
        As we can see, image (B) contains more cells which has resulted from a division process that
        is not yet occurred in image (A).
        In (C) we can see the "naive" comparison, simply identifying non-matching colors.
        By assigning penalties to all highlighted pixels, we would not take into consideration the
        parental relationship.
        This approach is displayed in (D) where pixels of cells that are related have been colored
        in gray.
    }
    \label{fig:mask-difference-metric}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]
        {../docs/source/_static/fitting-methods/penalty-time-flow.png}%
    \caption{
        Total cost between successive iteration steps $t_n,t_{n+1}$.
        The overall shape is expected to have the slope of an exponential function.
        We can clearly see that division events introduce jumps within this relationship.
        In the case where we account for the parental relationship, these jumps are mitigated.
        The penalty was set to $0$ for pixel-comparisons which belong to cells that are in a
        parental relationship.
    }
    \label{fig:penalty-calculation-cell-division}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.49\textwidth]
        {../docs/source/_static/scripts/crm_multilayer/multilayer-time-evolution.pdf}\\
    \includegraphics[width=0.49\textwidth]
        {../docs/source/_static/scripts/crm_multilayer/colony-height-vs-gel_pressure.pdf}
    \includegraphics[width=0.49\textwidth]
        {../docs/source/_static/scripts/crm_multilayer/colony-height-vs-time.pdf}
    \caption{TODO}
    \label{fig:multilayer}
\end{figure}

@@

%###################################################################################################
% EXCLUDE THIS FOR NOW
% \section{Plastic Deformations}
% 
% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.49\textwidth]
%         {../docs/source/_static/scripts/crm_amir/0000000023.png}\\
%     \includegraphics[width=0.49\textwidth]
%         {../docs/source/_static/scripts/crm_amir/angles.pdf}
%     \includegraphics[width=0.49\textwidth]
%         {../docs/source/_static/scripts/crm_amir/endpoints.pdf}
%     \caption{TODO}
%     \label{fig:amir}
% \end{figure}

\bibliographystyle{IEEEtran}
\bibliography{../docs/source/references}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.49\textwidth]
        {../docs/source/_static/performance/computation-time-with-initial-agents.pdf}
    \includegraphics[width=0.49\textwidth]{../docs/source/_static/performance/flamegraph.pdf}
    \caption{TODO}
    \label{fig:performance}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{docs/source/_static/mechanics.png}
    \caption{
        Example of an elonged bacterial rod represented by a collection of vertices which are
        connected by springs.
        The angles $\alpha_i$ have been exaggerated such that they can be identified more easily.
        A bacterial agent which is not interacting with any external objects will tend to the
        equilibrium state of a straight rod with $0$ curvature.
    }
    \label{fig:mechanics-bacterium}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/raw_pv/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/images/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/09395645494836445480/masks/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \caption{
        (A) shows the raw result from combining sphere and cylinder meshes to obtain the shape of a
        bacterial rod.
        This render contains lighting coming from 2 light sources which thus produces a small glow
        on the upper part of the meshes.
        Subfigure (B) takes this image and applies noise to it in order to make it look more
        like an actual microscopic image.
        (C) The render is projected along the z-axis and flat numerical values are assigned to the
        bacteria.
        The resuling render can have overlaps in which case the color of the rod is displayed that
        is higher along the z-direction.
    }
    \label{fig:progression-image-generation}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/algorithm/image001042.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/algorithm/mask-zoom.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/algorithm/mask-zoom.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \caption{
        TODO change 2nd image!\\
        (A) An example of a microscopic image.
        (B) The associated mask which assigns individual color values to each bacterium.
        (C) The result of the  skeletonization algorithm when applying it to a single cell.
    }
    \label{fig:position-extraction-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-004000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-006000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {docs/source/_static/fitting-methods/extract_positions-008000.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-calculations.png}%
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/displacement-distribution.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}
    \caption{
        Progression of generated masks with estimated and exact positions.
        Comparison of masks across generations. Compare estimated with exact rod lengths.
    }
    \label{fig:benchmarking-extraction-algorithm}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/fitting-methods/progressions-1.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/fitting-methods/progressions-2.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}
    \linebreak
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/fitting-methods/progressions-3.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {docs/source/_static/fitting-methods/progressions-4.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}
    \caption{
        The figure shows two masks (A,B) which will be compared against each other.
        As we can see, image (B) contains more cells which has resulted from a division process that
        is not yet occurred in image (A).
        In (C) we can see the "naive" comparison, simply identifying non-matching colors.
        By assigning penalties to all highlighted pixels, we would not take into consideration the
        parental relationship.
        This approach is displayed in (D) where pixels of cells that are related have been colored
        in gray.
    }
    \label{fig:mask-difference-metric}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]
        {docs/source/_static/fitting-methods/penalty-time-flow.png}%
    \caption{
        Total cost between successive iteration steps $t_n,t_{n+1}$.
        The overall shape is expected to have the slope of an exponential function.
        We can clearly see that division events introduce jumps within this relationship.
        In the case where we account for the parental relationship, these jumps are mitigated.
        The penalty was set to $0$ for pixel-comparisons which belong to cells that are in a
        parental relationship.
    }
    \label{fig:penalty-calculation-cell-division}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.49\textwidth]
        {docs/source/_static/scripts/crm_multilayer/multilayer-time-evolution.pdf}\\
    \includegraphics[width=0.49\textwidth]
        {docs/source/_static/scripts/crm_multilayer/colony-height-vs-gel_pressure.pdf}
    \includegraphics[width=0.49\textwidth]
        {docs/source/_static/scripts/crm_multilayer/colony-height-vs-time.pdf}
    \caption{TODO}
    \label{fig:multilayer}
\end{figure}

@@

%###################################################################################################
% EXCLUDE THIS FOR NOW
% \section{Plastic Deformations}
% 
% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/0000000023.png}\\
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/angles.pdf}
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/endpoints.pdf}
%     \caption{TODO}
%     \label{fig:amir}
% \end{figure}

\bibliographystyle{IEEEtran}
\bibliography{references}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.49\textwidth]
        {docs/source/_static/performance/computation-time-with-initial-agents.pdf}
    \includegraphics[width=0.49\textwidth]{docs/source/_static/performance/flamegraph.pdf}
    \caption{TODO}
    \label{fig:performance}
\end{figure}
